lab_notebook

### 2018-11-29 lab_notebook.Rmd
nothing
gdp data and start of logit

>>>>

###########
11/26/2018

species_rightsbased <- read_csv("data/species_rightsbased_binary.csv")

upside_2018_updated <- readRDS("/GitHub/global_fisheries_managment/processed_data/upside_2018_updated.rds")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

Part 4:
For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).

gdp <- filter(gdp_all, current_gdp != "NA")

join_gdp_rightsbased <- join(gdp, species_rightsbased, by = c("Country"), type = "full")

gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )

as_factor <- gdp_rightsbased$i_right
as_factor <- gdp_rightsbased$turf

itq_glm <- glm(i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
turf_glm
